\documentclass[100pt]{article}
\title{Experiment - 2} % Title
\date{9 feb.2017} % Date for the report
\begin{document}
		\maketitle % Insert the title, author and date
	\section{Aim}
    To study about MySQL Database and its properties.
	\section{Software used}
	MySQL Workbench
	\section{Theory}
     Essentially, where computers are concerned, a database is just a collection of data. Specialised (or "specialized" in US English) database software, like MySQL, are just programs that lets you store and retrieve that data as efficiently as possible.In computer science, ACID (Atomicity, Consistency, Isolation, Durability) is a set of properties of database transactions.Detail of these properties is given below - \\	
    \textbf{Atomicity}\\
    Atomicity requires that each transaction be "all or nothing": if one part of the transaction fails, then the entire transaction fails, and the database state is left unchanged. An atomic system must guarantee atomicity in each and every situation, including power failures, errors and crashes. To the outside world, a committed transaction appears to be indivisible, and an aborted transaction does not happen.\\
    \textbf{Consistency}\\
    The consistency property ensures that any transaction will bring the database from one valid state to another. Any data written to the database must be valid according to all defined rules, including constraints, cascades, triggers, and any combination thereof. This does not guarantee correctness of the transaction in all ways the application programmer might have wanted but merely that any programming errors cannot result in the violation of any defined rules.\\
    \newpage
    \textbf{Isolation}\\
    The isolation property ensures that the concurrent execution of transactions results in a system state that would be obtained if transactions were executed sequentially, i.e., one after the other. Providing isolation is the main goal of concurrency control. Depending on the concurrency control method,the effects of an incomplete transaction might not even be visible to another transaction.\\
    \textbf{Durability}\\
    The durability property ensures that once a transaction has been committed, it will remain so, even in the event of power loss, crashes, or errors. In a relational database, for instance, once a group of SQL statements execute, the results need to be stored permanently.To defend against power loss, transactions must be recorded in a non-volatile memory.\\
    
    \section{Procedure}
    1. Open MySQL workbench.\\
    2. Go to file option and open a new Query Tab.\\
    3. Write syntex for database creating as follows - \\
    
      \textbf{ CREATE DATABASE Database name }\\
      
    Database name should be unique and max upto 128 characters.\\
      for example-\\
                     CREATE DATABASE MOHIT\\
    4. Finally execute the written code for the output.  \\
   
    
    
   \section{Result}
   A new database namely MOHIT is created and its properties are studied successfully.
\end{document}