\documentclass[50pt]{article}
\title{Experiment - 1} % Title
\date{2 feb.2017} % Date for the report

\begin{document}
		\maketitle % Insert the title, author and date
	\section{Aim}
     Installation of MySQL Workbench
	\section{Software used}
	Microsoft .NET Framework 4.5, Microsoft Visual C++ 2015 Redistributable Package
	\section{Theory}
	MySQL Workbench is a unified visual tool for database architects, developers, and DBAs. MySQL Workbench provides data modeling, SQL development, and comprehensive administration tools for server configuration, user administration, backup, and much more. MySQL Workbench is available on Windows, Linux and Mac OS X.\\
    MySQL offers standard database driver connectivity for using MySQL with applications and tools that are compatible with industry standards ODBC and JDBC.	MySQL Workbench enables a DBA, developer, or data architect to visually design, model, generate, and manage databases.	MySQL Workbench delivers visual tools for creating, executing, and optimizing SQL queries.MySQL Workbench provides a visual console to easily administer MySQL environments and gain better visibility into databases. Developers and DBAs can use the visual tools for configuring servers, administering users, performing backup and recovery, inspecting audit data, and viewing database health.\\
	As there are a lot of health care data.To handle these data MySQL workbench is playing a very impotant role.
    \section{Procedure}
    MySQL Workbench may be installed using the Windows installer file or it may be installed manually from a ZIP file.\\
    \newpage
   \textbf{ Installing MySQL Workbench Using the Installer}\\
    MySQL Workbench can be installed using the Windows Installer (.msi) installation package. To install MySQL Workbench,\\
    1. Right-click the MSI file and select the Install option from the pop-up menu, or simply double-click the file.\\
    2. In the Setup Type window you may choose a Complete or Custom installation. To use all features of MySQL Workbench choose the Complete option.\\
    3. Unless you choose otherwise, MySQL Workbench is installed in C:\%PROGRAMFILES%\MySQL\MySQL Workbench 5.1 edition_type\, where %PROGRAMFILES% is the default directory for programs for your locale. The %PROGRAMFILES% directory may be C:\Program Files or C:\programme.
    
   \textbf{ Installing from the ZIP File}\\
    If you are having problems running the installer, as an alternative, you can download a ZIP file without an installer. That file is called mysql-workbench-version-win32.zip. Using a ZIP utility, unpack it to the directory of your choice. You may also want to create a shortcut on your desktop or the quick launch bar.
    To install using the ZIP file,\\
     Download the ZIP file to a convenient location and decompress the file. You can place the resulting directory anywhere on you system. You do not need to install or configure the application before using it.
   \section{Result}
   MySQL workbench was successfully installed on windows 10
\end{document}